---
title: "Introduction"
author: "Casey Chadwell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, error=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
```

# Binomial Package
This package is my __workout 3__ assignment for the Stat 133 class at UC Berkeley. The package contains functions, objects, and methods for binomial distributions.

## Basic Calculations

The most basic use of this package is to calculate statistics on binomial distributions such as mean, variance, mode, skewness, and kurtosis. 

```{r}
# set a number of trials and probability of success per trial
num_trials <- 5
prob_success <- 0.7
```

#### Mean
```{r}
bin_mean(num_trials, prob_success)
```

#### Variance
```{r}
bin_variance(num_trials, prob_success)
```

#### Mode
```{r}
bin_mode(num_trials, prob_success)
```

#### Skewness
```{r}
bin_skewness(num_trials, prob_success)
```

#### Kurtosis
```{r}
bin_kurtosis(num_trials, prob_success)
```

For these summary measures, note that the probability must be between 0 and 1 and the number of trials must be a nonnegative integer. If the input is invalid, an error message will be displayed. 

```{r error = TRUE}
# This will return an error
bin_mean(-5, 0.5)

# This will also return an error
bin_kurtosis(1, 100)
```

## Creating Distribution Objects

This package can also be used to create 2 different distribution objects, "bindis" and "bincum" that both inherit from "data.frame". 

#### Binomial Distribution

`"Binomial distribution"` objects are displayed like `data.frame` objects with columns `successes`, `probability` that shows the probability that the specified number of successes will be achieved in the trials. 
```{r}
# Setting the Distribution Arguments
num_trials <- 5
prob_success <- 0.5

# Creating a Binomial Distribution Object
basic_dist <- bin_distribution(num_trials, prob_success)

# "bindis" displays like a data.frame
basic_dist
```

This object can be plotted using `plot`. 

```{r}
# uses S3 generic method for plot
plot(basic_dist)
```

#### Cumulative Binomial Distribution

`"Cumulative Binomial Distribution"` objects are very similar to `"Binomial Distribution"` objects but with a third column showing the cumulative probability. 

```{r}
# Creating a Cumulative Binomial Distribution Object
basic_cum <- bin_cumulative(num_trials, prob_success)

# "bincum" displays like a data.frame
basic_cum
```

The "bincum" object is also plotted using `plot`, but the mode of plotting is different than with "bindis".

```{r}
# uses S3 generic method for plot 
plot(basic_cum)
```

## Binomial Variable Object

Finally, this package includes a `"Binomial Variable"` object of class `"binvar"` that represents the random variable for a binomial distribution. To initialize a `"binvar"` object, simply call the `bin_variable` function. 

```{r}
# Create the object
basic_var <- bin_variable(num_trials, prob_success)

# Display the object
basic_var
```

For easy viewing of the properties of your random variable, you can use the `summary` function. 

```{r}
# make summary
basic_sum <- summary(basic_var)

# Display summary
basic_sum
```
